% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass[margin]{res} 
% the margin option causes section titles to appear to the left of body text 
\textwidth=5.2in % increase textwidth to get smaller right margin
\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 

\begin{document} 
 
\name{Utkarsh Patange\\[12pt]} % the \\[12pt] adds a blank line after name
 
\address{{\bf Present Address} \\ Room 101, Hall 3 \\ IIT Kanpur, Kanpur  \\ Uttar Pradesh 208 016 \\
        +919651743002 }
\address{{\bf Permanent Address} \\ Sahyadri Hospital, wadia factory area\\ Shivaji Nagar, Nanded\\ Maharashtra 431 602\\
        +91 (2462) 230597 }

 
\begin{resume} 
 
\section{Objective} 
Summer position that will use my computer skills.

\section{Education} 
Indian Institute of Technology Kanpur\\
                BTech. in CSE, expected July 2015 \\
                G.P.A. 9.4/10.0 
 
                \begin{tabular}{ l c }
               
                {\bf Major Subjects}   &  {\bf Grade} \\
                Data Structures and Algorithms           &  A \\
                Intro. to Computer Organisation &  A \\
                Computing Laboratory I-II        & A \\
                Mathematics in Comp. Science  & A \\
                Abstract Algebra   &  A \\
                Logic in Comp. Science &  A\\
		\end{tabular}

\section{Experience}
{\bf Project,} Surge project under Prof. Ajai Jain \hfill
Summer 2013                
                \begin{itemize} \itemsep -2pt
                 \item Developed an algorithm to find the Shortest time path in a Railway Network.
                
                 \item Implemented the algorithm in C++ platform

		 \end{itemize}

{\bf Assignment,} As part of Introduction to Computer Organization course \hfill 2012-13
		\begin{itemize} \itemsep -2pt
		\item Made a General Purpose Computer to run small programs on an FPGA kit
		\item Implemented as a Finite State Machine in Verilog
\end{itemize}				 
{\bf Assignment,} As part of Computing Laboratory course \hfill  2012-13
\begin{itemize} \itemsep -2pt %reduce space between items
\item Created an Online Room Allocation Facility
\item Log-in based system
\item Appropriate priority assigned according to nature of applicant (Professor, Gymkhana member or Club Co-ordinator)
\end{itemize}



 {\bf Project,} ACA project under ACA co-ordinator Pankaj Jindal \hfill 2011-12
 \begin{itemize} \itemsep -2pt  % reduce space between items
 \item Created an encrypted chat client.
 \item RSA encoding was used in C language.
 \end{itemize}

 
 

\section{Leadership Activities} 
               {\bf Co-ordinator,} India Haat, Antaragni '13    \hfill         2013
          \begin{itemize}\itemsep -2pt
          
          
               \item Responsible for conduct of major event India Haat in Antaragni '13.
               \item India Haat is a cultural event promoting Indian culture.
          \end{itemize}

		{\bf Co-ordinator,} Chess, Udghosh '12 \hfill   2012 
                \begin{itemize} \itemsep -2pt
                 \item  Responsible for conduce of Chess event in Udghosh '12.
                
                
		 \end{itemize}

\section{Academic Achievements} 
Academic Excellence Award 2012-13 \\
SURGE '13 fellowship \\
Secured All India Rank 150 in IIT-JEE 2011 \\
KVPY 2009 fellowship

% Tabulate Computer Skills; p{3in} defines paragraph 3 inches wide
\section{Technical \\ Skills}
   \begin{tabular}{l p{3in}}
    \underline{Languages:} & C++, Python, HTML, MySQL, Verilog \\

     \underline{Tools:} &  \LaTeX, Flex and Bison
 \end{tabular}

\end{resume} 
\end{document} 



